---

title       : Dataset Exploration
substitle   : Perusing 'datasets' R Library
author      : Conrad Warmbold
job         : 
framework   : io2012
highlighter : highlight.js
widgets     : []
mode        : selfcontained
 
--- 

The 'datasets' library contains the following datasets -- which one should you use?

```{r, echo=FALSE}
library(datasets)
datasets <- sapply(subset(data.frame(data()$results), Package=='datasets')$Item, as.character)
for (i in 1:length(datasets)) {
    datasets[i] <- unlist(strsplit(datasets[i], ' '))[1] # Strip trailing (explanation)
}
print(datasets)
```

---

While learning R, I've created an app to help you explore each of the 'datasets' items.  From dropdowns, you can select both a dataset and a function to apply to that dataset:

```{r, echo=FALSE}
c('summary', 'str', 'head', 'tail', 'print', 'class', 'names')
```

---

Additionally, when a dataset is selected, its default table and plot are rendered.  Datasets that don't render directly are manually coerced as shown below:

```{r, eval=FALSE}
if (class(dataset) %in% c('ts', 'list', 'table', 'factor', 'numeric', 'character')) { 
    dataset <- as.data.frame(dataset)
}
```

---

Visit the [Data Exploration](https://cradbold.shinyapps.io/devdataprod-005/) now to see it in action!
